Chemical Tagging Using Minimum Message Length

### 2017-04-13 articles/chemical-tagging/ms.tex
add the 12 disciples :praying:

@@

% First formulate the problem: what is needed to make things work?

@@

\begin{equation}
    p(\bm{\mu},\bm{\Sigma}) \propto |C|^{\frac{d + 1}{2}} \right.
\end{equation}
% TODO: DERIVE THIS.

>>>>

% Have some maaaath.
\def\infinity{\rotatebox{90}{8}}

@@

What is needed to make things work? We outline the 12 disciples:

\begin{enumerate}
\item The number of clusters.
\item The number of latent factors (e.g., supernovae yields, AGB yields).
\item The multivariate factor loads of individual latent factors.
\item The relative weighting (yet another latent factor, which is however not
      common between all mixtures) of individual mixtures.
\item The relative \emph{scoring} of different latent factors on each star.
\item The intrinsic \emph{specific variances} of the individual abundances.
\item The multivariate mean abundances and covariance matrices of each star
      cluster, where the covariance matrix includes off-diagonal terms that
      describe the \emph{data} correlations (e.g., the correlations that result
      from trying to measure multiple abundances from the same data).
\item Atomic diffusion, veiling, and thermohaline mixing: The surface chemical
      abundances of stars \emph{will change} over its lifetime.
\item Probabilistic priors (perhaps very hard priors) on joint responsibilities
      of stars that are specified from astrometric constraints.
\item There are missing data. Accept it.
\item There are \emph{upper limits} on some data.\footnote{
        Spectroscopists are probably the worst in the Universe when it comes to
        reporting upper limits. They will report an `\emph{upper limit}', when
        what might mean is the \emph{absolute limit} where there is zero
        likelihood that the true value is above the given point estimate (which might as well be $+\infinity$, or
        they may describe a \emph{pseudo-1$\sigma$} limit which is estimated
        from the locally (yet covariant!) heteroskedastic noise in the data (which often might as well be $\approx$0).
        In reality, an upper limit ought to be given as a probability density
        function that is skewed in one direction, perhaps similar to the shape
        of a log-normal distribution. In any case, the confidence to which they
        describe their `\emph{upper limit}' ought to be given.}
\item There are correlations in the measurements that result from trying to
      measure two (or more) abundances from the same data. As an example,
      consider a rare -- yet important -- chemical abundance that has a single
      atomic absorption line which is blended with a more common elemental
      abundance. In all likelihood, there will be a strong positive correlation
      between the abundance derived between the rare and more common elemental
      abundance.
\end{enumerate}

@@

\begin{equation}
    p(\bm{\mu},\bm{\Sigma}) \propto |C|^{\frac{d + 1}{2}} 
\end{equation}
% TODO: DERIVE THIS.
